A thesis draft

### 2018-11-21 res/sections/10-ProjectAnalysis.tex
Add bib and initial description

\subsubsection{OpenvSwitch} \todo{Talk about OpenvSwitch!!}
\subsubsection{Openbaton}
\label{chap:prjan:sec:tech:sub:other:sub:openbaton}
Patronized by the Institute Fraunhofer, it's a open-source, customizable NFV 
MANO-compliant framework, that offers many configurations options, and since 
it's 
written in Java, there is the possibility to add components (plug-ins) 
dynamically. Openbaton can be installed as a normal computer program (they 
offer packages for the most common distros) but it can be deployed on Docker 
containers too. It's designed to work with cloud providers like Amazon or 
Google Compute engine, but it offers compatibility with on-premise cloud 
solutions like Openstack, where it deploys virtual machines using the API
the platform offers. It can store VNF configurations saved as TOSCA
YAML\todo{What does TOSCA mean? Find out} and it can handle multiple
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecycle management
out-of-the-box, with the possibility to customize it based on the user needs.
Its modular design allows developers to change parts of the codebase with custom
ones, making the product really flexible to different platforms. Performing this
operation requires a deep knowledge of the framework though.
\begin{figure}[h]
 \centering \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}

>>>>

\subsubsection{OpenvSwitch} \todo{Talk about OpenvSwitch!!}

\subsubsection{Floodlight}
\label{chap:prjan:sec:tech:sub:other:sub:floodlight}
Community-developed and open source, Floodlight is an OpenFlow Controller
written in Java born in 2011~\cite{floodlightGit}. It allows various
applications to run on top of it. Floodlight has the role of controlling and
inquiring an OpenFlow network, querying the applications integrated with the
purpose of solving different user needs over the network. When instantiated,
OpenSwitch routers have to register to the controller in order to gain routing
rules from the controller.

\subsubsection{Openbaton}
\label{chap:prjan:sec:tech:sub:other:sub:openbaton}
Patronized by the Institute Fraunhofer, it's a open-source, customizable NFV 
MANO-compliant framework, that offers many configurations options, and since 
it's 
written in Java, there is the possibility to add components (plug-ins) 
dynamically. Openbaton can be installed as a normal computer program (they 
offer packages for the most common distros) but it can be deployed on Docker 
containers too. It's designed to work with cloud providers like Amazon or 
Google Compute engine, but it offers compatibility with on-premise cloud 
solutions like Openstack, where it deploys virtual machines using the API
the platform offers. It can store VNF configurations saved as TOSCA
YAML\todo{What does TOSCA mean? Find out} and it can handle multiple
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecycle management
out-of-the-box, with the possibility to customize it based on the user needs.
Its modular design allows developers to change parts of the codebase with custom
ones, making the product really flexible to different platforms. Performing this
operation requires a deep knowledge of the framework though.
\begin{figure}[h]
 \centering \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}
